Probabilistic Programming

### 2014-04-21 paper/paper.tex
New screenshow to show syntax highlighting and depth toggle

In the current implementation of this system, following the paths [\emph{Identifier}, \emph{Name}], or [\emph{Literal}, \emph{Raw}] result not in node types, but rather in the text of the identifier names or literal values. This way, generating identifiers and literals is simply a probabilistic process like the rest of the code generation. Of course, this means that sometimes identifiers are added that are not in scope, that have mismatched types, or that simply make no semantic sense. (But adjusting $depth$ did seem to make programs more meaningful, expectedly. This can be seen experimentally on our web IDE, explained in Section 4.1.)

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.00\textwidth]{screenshot}
  \caption{Screenshot of the web program editor GUI} \label{fig:screenshot}
\end{figure}

>>>>

In the current implementation of this system, following the paths [\emph{Identifier}, \emph{Name}], or [\emph{Literal}, \emph{Raw}] result not in node types, but rather in the text of the identifier names or literal values. This way, generating identifiers and literals is simply a probabilistic process like the rest of the code generation. Of course, this means that sometimes identifiers are added that are not in scope, that have mismatched types, or that simply make no semantic sense. (But adjusting $depth$ did seem to make programs more meaningful, as expected. This can be seen experimentally by modifying depth on our web IDE, which explained in Section 4.1.)

@@

\begin{figure}[h]
  \centering
  \includegraphics[width=1.00\textwidth]{ide}
  \caption{Screenshot of the web program editor GUI} \label{fig:screenshot}
\end{figure}
